other functionalities

### 2019-08-06 inst/gitbook/05_other-functionalities.Rmd
slide.nodes!

>>>>

## `slide.nodes`

This function allows to slide nodes along a tree!
In other words it allows to change the branch length leading to a node without modifying the overall tree shape.
This can be useful to add some value to 0 branch lengths for example.

The function works by taking a node (or a list of nodes), a tree and a sliding value.
The node will be moved "up" (towards the tips) for the given sliding value.
You can move the node "down" (towards the roots) using a negative value.

```{r}
set.seed(42)
## Generating simple coalescent tree
tree <- rcoal(5)

## Sliding node 8 up and down
tree_slide_up <- slide.nodes(8, tree, slide = 0.075)
tree_slide_down <- slide.nodes(8, tree, slide = -0.075)

## Display the results
par(mfrow = c(3,1))
plot(tree, main = "original tree") ; axisPhylo() ; nodelabels()
plot(tree_slide_up, main = "slide up!") ; axisPhylo() ; nodelabels()
plot(tree_slide_down, main = "slide down!") ; axisPhylo() ; nodelabels()
```
